Chapter3_ideas

### 2019-12-05 results/Chapter3_ideas.Rmd
added in data to start recreating Wang et al findings

---
title: "Chapter3_ideas"
author: "April Peterson"
date: "November 26, 2019"
output: html_document
---

```{r setup, include=FALSE}
#load biv data
#load MLH1 data
library(dplyr)
library(plyr)
library(ggplot2)

@@

@@

```{r choosing.mice, echo=FALSE, eval=FALSE}
#Choose mice with many cells

@@

shiz <- ggplot(data = MLH1_data[MLH1_data$mouse == "31may19_SKIVE_f6",],
       aes(x=nMLH1.foci))+geom_histogram(stat = "bin", binwidth = 1)+ggtitle("31may19_SKIVE_f6 Cell counts")+
geom_vline(xintercept = c(min(high.bin), max(low.bin)), color= "red")
#highest of the low bin
#lowest value of the high bin
shiz
#get the filenames for this groups of cells

@@

@@

```{r whole.cell.data, echo=FALSE}

@@

#load main data file
whole.cell.data <- read.csv("~./MLH1repo/whole_cell_measures.csv")

@@

biv.count_table <-  ddply(.data=whole.cell.data,
                 .(fileName),
                 summarize,
                 nbiv = length(SC.length)
)
#all have 20 or 19 (after removing XY)

#ADD THE RANK
for(musy in as.character(unique(whole.cell.data$fileName))){
  print(musy)

@@

Try doing the permutations

```{r permutations.sc, echo=FALSE}

male.whole.cell <- whole.cell.data[whole.cell.data$sex == "male", ]#359
#ncells
length(unique(male.whole.cell$fileName) ) #24 cells

female.whole.cell <- whole.cell.data[whole.cell.data$sex == "female", ]#456
length(unique(female.whole.cell$fileName) ) #18 cells

male.biv.count_table <-  ddply(.data=male.whole.cell,
                 .(fileName),
                 summarize,
                 nbiv = length(SC.length),
                 mean_co = mean(hand.foci.count),
                 mean_sc = mean(SC.length),
                   var_co = var(hand.foci.count),
                   var_sc = var(SC.length)
)

```{r per.co.count, echo=FALSE}

iterations = 24
variables = 20
DF.permutations_CO.count <- matrix(ncol=variables, nrow=iterations)
colnames(DF.permutations_CO.count) <- c("1", "rank1", "rank2", "rank3", "rank4", "rank5",
                               "rank6","rank7","rank8","rank9","rank10","rank11",
                               "rank12","rank13","rank14","rank15","rank16",
                               "rank17","rank18","rank19" )

@@

#plot
whole.cell.var_CO.plot  <- ggplot(co.var.for.plot, aes(y=var, x=type))+geom_jitter()+ggtitle("within cell CO variance")
whole.cell.var_CO.plot

@@

```{r permuted.v.real, echo=FALSE}
#evaluating the permuted 
library(plyr)

for( o in 1:nrow(DF.permutations_CO.count) ) {
  DF.permutations_CO.count$var_CO.count[o] <- var(as.numeric(DF.permutations_CO.count[o,2:20]))
  }

@@

```{r junk, eval=FALSE}
DF.permutations <- data.frame( nuc.sim = seq(1:24), rank1 = replicate(24, ""),rank2= replicate(24, ""),
                       rank3= replicate(24, ""),     rank4= replicate(24, ""),
                       rank5= replicate(24, ""),   rank6= replicate(24, ""),
                       rank7= replicate(24, ""), rank8= replicate(24, ""),
                       rank9= replicate(24, ""), rank10= replicate(24, ""),
                       rank11= replicate(24, ""),     rank12= replicate(24, ""),
                       rank13= replicate(24, ""),     rank14= replicate(24, ""),
                       rank15= replicate(24, ""),     rank16= replicate(24, ""),
                       rank17= replicate(24, ""),rank18= replicate(24, ""),rank19= replicate(24, "")
                       )
```

>>>>

---
title: "Chapter3_ideas"
author: "April Peterson"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

```{r setup, include=FALSE}
#load biv data
#load MLH1 data
library(dplyr)
library(plyr)
library(ggplot2)
library(reshape2)
library(raster) #cv

#read files
whole.cell.data <- read.csv("~./MLH1repo/whole_cell_measures.csv")
load(file="~./MLH1repo/data/CleanBivData.RData")#added batch17

@@

# Summary and recreation of Wang et al 2019

insert summary of the Wang paper

which data did they use? what summary stat were they comparing
What were their results?

human data- 
Gruhn et al 2013 (ploted below)
Sun et al 2006
Oliver-Bonet et al 2007 
Lian et al 2008
Lu et al 2012
Hou et al 2013

```{r human.male.data, echo=FALSE}
#read files
Hs.male_axis <- read.csv("~./MLH1repo/data/Human_male_axis_length.csv", header = TRUE)
Hs.male_MLH1 <- read.csv("~./MLH1repo/data/Human_male_MLH1.csv", header = TRUE)
#I assume that the rows of MLH1 and SC lengths are the linked observations, check or verify this assumption
#if they are using within cell -- they must

#melt DF -- how do I keep row.name info?
Melted.Hs.male_axis <- melt(Hs.male_axis, 
                            c("row.name", "chr1","chr2","chr3",  "chr4",  "chr5",  "chr6",  "chr7",  "chr8",  "chr9",  "chr10", "chr11", "chr12", "chr13", "chr14", "chr15", "chr16", "chr17", "chr18", "chr19", "chr20", "chr21", "chr22"), 
                         id=c("row.name") )
#remove the first part with of data frame, variable = "row.name""

#clean up dm1 (there are a bunch of rows without useful information)
Melted.Hs.male_axis <- Melted.Hs.male_axis[(!is.na(Melted.Hs.male_axis$value)),]
Melted.Hs.male_axis <- Melted.Hs.male_axis[((Melted.Hs.male_axis$variable != "row.name")),]

colnames(Melted.Hs.male_axis) <- c("row.name", "Chrm.id", "axis.length")

#Seems like there is an outlier, 
Melted.Hs.male_axis <- Melted.Hs.male_axis[(Melted.Hs.male_axis$axis.length < 700 ),]

hs.sc.length_plot <- ggplot(Melted.Hs.male_axis, aes(y=axis.length, x=Chrm.id))+geom_jitter(aes( color=row.name, alpha = .2))+geom_boxplot()+ 
  ggtitle("Human male SC Lengths")+theme(legend.position="none")
hs.sc.length_plot

Neat. cool to see human SC data plotted. One outlier was removed.

# Adding to whole Cells

Look/use the DF, Curated_BivData

@@

Chunk below has code for choosing mice with a good number of cells (25?)

```{r choosing.mice, echo=FALSE, eval=FALSE}
#Choose mice with many cell observations 
#important for increased power for within mouse variance

@@

shiz <- ggplot(data = MLH1_data[MLH1_data$mouse == "31may19_SKIVE_f6",],
       aes(x=nMLH1.foci))+geom_histogram(stat = "bin", binwidth = 1)+ggtitle("31may19_SKIVE_f6 Cell counts")+
geom_vline(xintercept = c(min(high.bin), max(low.bin)), color= "red")
#highest of the low bin
#lowest value of the high bin

#get the filenames for this groups of cells

@@

from the curated BivData, figure out which can be added / into the whole cell data. I think there might only be a couple cell to add in.

```{r add.more.whole.cell, echo=FALSE}

#load data curatedBiv Data
#load in hand measures

@@

```{r setup.whole.cell.data, echo=FALSE}

@@

@@

#ADD THE RANK
for(musy in as.character(unique(whole.cell.data$fileName))){
  #print(musy)

@@

## Adding to whole cell measures

calculated the observed values in this chunk.

```{r cell.level.tables, echo=FALSE}

whole.cell.data <- whole.cell.data[(whole.cell.data$hand.foci.count!="XY"), ]

male.whole.cell <- whole.cell.data[whole.cell.data$sex == "male", ]#359
#ncells
#length(unique(male.whole.cell$fileName) ) #24 cells

female.whole.cell <- whole.cell.data[whole.cell.data$sex == "female", ]#456
#length(unique(female.whole.cell$fileName) ) #18 cells

biv.count_table <-  ddply(.data=whole.cell.data,
                 .(fileName),
                 summarize,
                 nbiv = length(SC.length)
)#all have 20 or 19 (after removing XY)

#real data
male.biv.count_table <-  ddply(.data=male.whole.cell,
                 .(fileName),
                 summarize,
                 nbiv = length(SC.length),
                 mean_co = mean(hand.foci.count, rm.na = TRUE),
                 mean_sc = mean(SC.length),
                   var_co = var(hand.foci.count),
                   var_sc = var(SC.length),
                 cv_co.count = cv(hand.foci.count),
                 cv_SC.length = cv(SC.length)
)

female.biv.count_table <-  ddply(.data=female.whole.cell,
                 .(fileName),
                 summarize,
                 nbiv = length(SC.length),
                 mean_co = mean(hand.foci.count),
                 mean_sc = mean(SC.length),
                   var_co = var(hand.foci.count),
                   var_sc = var(SC.length),
                 cv_co.count = cv(hand.foci.count),
                 cv_SC.length = cv(SC.length)
)#one of the female cells is missing values

# Plots of whole cell data

show SC length (y) by rank  (x), facet (sex)

```{r play.plots, echo=FALSE}
#female.whole.cell
#male.whole.cell

female.whole.cell <- female.whole.cell[!(is.na(female.whole.cell$SC.length) | female.whole.cell$SC.length==""), ]

cow.hugger <- ggplot(female.whole.cell, aes(x=rank, y=SC.length, color=mouse) ) +geom_jitter()

rank.length.boxplot <- ggplot(data=female.whole.cell) + geom_boxplot( aes(x=as.factor(rank), y=SC.length, fill=rank) )+geom_jitter(aes(x=as.factor(rank), y=SC.length) )+ggtitle("blaah")

rank.length.boxplot.xx <- ggplot(data=female.whole.cell, aes(x=as.factor(rank), y=SC.length) ) + geom_boxplot()+ geom_jitter(aes( color=fileName))+
  ggtitle("Female SC Length Dist by ranks")+theme(legend.position="none")

rank.length.boxplot.xy <- ggplot(data=male.whole.cell, aes(x=as.factor(rank), y=SC.length)) + geom_boxplot()+ geom_jitter(aes( color=fileName)) +ggtitle("Male SC Length Dist by ranks")+theme(legend.position="none")

rank.length.boxplot.xx
rank.length.boxplot.xy

# PERMUTATION SETUP

```{r per.co.count, echo=FALSE, eval=FALSE}
#I don't think ... I end up useing these (matrics / DFs)
iterations = 24
variables = 20
DF.permutations_CO.count <- matrix(ncol=variables, nrow=iterations)
colnames(DF.permutations_CO.count) <- c("1", "rank1", "rank2", "rank3", "rank4", "rank5",
                               "rank6","rank7","rank8","rank9","rank10","rank11",
                               "rank12","rank13","rank14","rank15","rank16",
                               "rank17","rank18","rank19" )

@@

#plot
#whole.cell.var_CO.plot  <- ggplot(co.var.for.plot, aes(y=var, x=type))+geom_jitter()+ggtitle("within cell CO variance")
#whole.cell.var_CO.plot

@@

## CO count, male

Make list of DFs to fill with permutations

```{r list.of.DF,echo=FALSE}

#dataframes to recreate -- and fill with 
#24 rows (cells/in silico nuclei) by 19 cols, (bivalent traits)

#make subsampled piece of DF here -- these are taking the whole DF
#I will just take single values
#Curated_BivData[ sample( which(Curated_BivData$category=="WSB female"), Biv.sample.Number ), ]
#male.whole.cell
#rand.rank.co <- sample(male.whole.cell$hand.foci.count[male.whole.cell$rank == col.num-1], 1, replace = FALSE)

#rank (sample all of the ranks then stich them together)
BIG.LIST_w.rank <- replicate(1000,
  list(bind_rows(list( 
  male.whole.cell[ sample( which(male.whole.cell$rank==1), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==2), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==3), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==4), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==5), 1, replace = FALSE ),],
   male.whole.cell[ sample( which(male.whole.cell$rank==6), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==7), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==8), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==9), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==10), 1, replace = FALSE ),],

   male.whole.cell[ sample( which(male.whole.cell$rank==11), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==12), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==13), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==14), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==15), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==16), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==17), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==18), 1, replace = FALSE ),],
  male.whole.cell[ sample( which(male.whole.cell$rank==19), 1, replace = FALSE ),]
))))
#this is replicating single cell (NOT a SAMPLE of 24)

#LIST of DF, no rank (include all), samples all 19 bivs at a time
#makes a list of 10 -- [[]]
BIG.DF.LIST_no.rank <- replicate(1000,
                  list(bind_rows(list( 
          male.whole.cell[ sample( which( male.whole.cell$rank < 20), 19, replace = FALSE ),]
) ) ) )

#dealing with lists of DFs, 
#2. #Loop through the list of DFs and do the ... make the cell level cVs calculations
#i is this index of the dataframes in the list?

#Calq cV for the rank perm
cv.val.DF_rank <- data.frame(  cV_co.count_rank = rep(0, length(BIG.LIST_w.rank) ) ) #first initialize the DF results will go in outside of loop
for(j in 1:length(BIG.LIST_w.rank)){  #inside loop, move thru the LISTs of DFs
 # print(j)
  #fill in the cells of given index
  cv.val.DF_rank$cV_co.count_rank[j] <-cv(  BIG.LIST_w.rank[[j]]$hand.foci.count )
  }

#Calq cV for no rank
cv.val.DF_no.rank <- data.frame(  cV_co.count_no.rank = rep(0, length(BIG.DF.LIST_no.rank) ) ) #first initialize the DF results will go in outside of loop
for(i in 1:length(BIG.DF.LIST_no.rank)){  #inside loop, move thru the LISTs of DFs
  #print(i)
  #fill in the cells of given index
  cv.val.DF_no.rank$cV_co.count_no.rank[i] <-cv(  BIG.DF.LIST_no.rank[[i]]$hand.foci.count )
  }
#extract the 
#next step make cell-level calqs of cV -- for plotting

#merge + plots of the cvs
#10 and 10 rows from the permuted
cv.val.DF_rank$type <- "sim w.rank"
colnames(cv.val.DF_rank) <- c("cV","type" )

cv.val.DF_no.rank$type <- "sim no rank"
colnames(cv.val.DF_no.rank) <- c("cV", "type")

#then add the real values
real.vals.cv.co <- data.frame(male.biv.count_table$cv_co.count)
real.vals.cv.co$type <- "real"
colnames(real.vals.cv.co) <- c("cV", "type")

#merge
cVs_permutations.DF <- rbind(cv.val.DF_rank, cv.val.DF_no.rank, real.vals.cv.co)

# need to melt the DFs before ploting?
#ploting --- plot with more sims
oo.plot <- ggplot(cVs_permutations.DF, aes(y = cV, x=type) )+ geom_jitter()+ ggtitle("cv for cell co count, 1000 simulated")

#  geom_histogram(bins = 50)+facet_wrap(.~Test.type, scales = "free")

#biggie <- ggplot(Melted.pval.DF, aes(pval) )+geom_histogram(bins = 50)+facet_wrap(.~Test.type, scales = "free") + ggtitle("pvalues for 1000 replicated t.tests")

The above plot the real data might have more variance because it's a combination of strains

## CO count, female

```{r CO.count.female, echo=FALSE}

#dataframes to recreate -- and fill with 
#24 rows (cells/in silico nuclei) by 19 cols, (bivalent traits)

#make subsampled piece of DF here -- these are taking the whole DF
#I will just take single values
#Curated_BivData[ sample( which(Curated_BivData$category=="WSB female"), Biv.sample.Number ), ]
#male.whole.cell
#rand.rank.co <- sample(male.whole.cell$hand.foci.count[male.whole.cell$rank == col.num-1], 1, replace = FALSE)

#rank (sample all of the ranks then stich them together)
BIG.LIST_w.rank_female <- replicate(1000,
  list(bind_rows(list( 
  female.whole.cell[ sample( which(female.whole.cell$rank==1), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==2), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==3), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==4), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==5), 1, replace = FALSE ),],
   female.whole.cell[ sample( which(female.whole.cell$rank==6), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==7), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==8), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==9), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==10), 1, replace = FALSE ),],

   female.whole.cell[ sample( which(female.whole.cell$rank==11), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==12), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==13), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==14), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==15), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==16), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==17), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==18), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==19), 1, replace = FALSE ),],
  female.whole.cell[ sample( which(female.whole.cell$rank==20), 1, replace = FALSE ),]
  ))))

#LIST of DF, no rank (include all), samples all 19 bivs at a time
#makes a list of 10 -- [[]]
BIG.DF.LIST_no.rank_female <- replicate(1000,
                  list(bind_rows(list( 
          female.whole.cell[ sample( which( female.whole.cell$rank < 20), 20, replace = FALSE ),]
) ) ) )

These permuted dataframes can be reused for all the meiotic traits, (CO.count, SC length, and position).

```{r sum.stat_cv.CO, echo=FALSE}
#CALUCULATING SUMMARY STAT from the permuted DFs
#dealing with lists of DFs, 
#2. #Loop through the list of DFs and do the ... make the cell level cVs calculations
#i is this index of the dataframes in the list?

#Calq cV for the rank perm
cv.val.DF_rank.female <- data.frame(  cV = rep(0, length(BIG.LIST_w.rank_female) ) ) #first initialize the DF results will go in outside of loop
for(j in 1:length(BIG.LIST_w.rank_female)){  #inside loop, move thru the LISTs of DFs
 # print(j)
  #fill in the cells of given index
  cv.val.DF_rank.female$cV[j] <-cv(  BIG.LIST_w.rank_female[[j]]$hand.foci.count ) #for each
  }

#Calq cV for no rank
cv.val.DF_no.rank.female <- data.frame(  cV = rep(0, length(BIG.DF.LIST_no.rank_female) ) ) #first initialize the DF results will go in outside of loop
for(i in 1:length(BIG.DF.LIST_no.rank_female)){  #inside loop, move thru the LISTs of DFs
  #print(i)
  #fill in the cells of given index
  cv.val.DF_no.rank.female$cV[i] <-cv(  BIG.DF.LIST_no.rank_female[[i]]$hand.foci.count ) #for each 
}

#merge + plots of the cvs
#10 and 10 rows from the permuted
cv.val.DF_rank.female$type <- "sim w.rank"
colnames(cv.val.DF_rank) <- c("cV","type" )

cv.val.DF_no.rank.female$type <- "sim no rank"
colnames(cv.val.DF_no.rank.female) <- c("cV", "type")

#then add the real values
real.vals.cv.co_female <- data.frame(female.biv.count_table$cv_co.count)
real.vals.cv.co_female$type <- "real"
colnames(real.vals.cv.co_female) <- c("cV", "type")

#merge
cVs_permutations.DF_female <- rbind(cv.val.DF_rank.female, cv.val.DF_no.rank.female, real.vals.cv.co_female)

# need to melt the DFs before ploting?
#ploting --- plot with more sims
Femaleplot_cV <- ggplot(cVs_permutations.DF_female, aes(y = cV, x=type) )+ geom_jitter()+ ggtitle("cv for cell co count female, 1000 simulated")

#  geom_histogram(bins = 50)+facet_wrap(.~Test.type, scales = "free")

#biggie <- ggplot(Melted.pval.DF, aes(pval) )+geom_histogram(bins = 50)+facet_wrap(.~Test.type, scales = "free") + ggtitle("pvalues for 1000 replicated t.tests")

cVs_permutations.DF$sex <- "male"
cVs_permutations.DF_female$sex <- "female"

all.cv <- rbind(cVs_permutations.DF, cVs_permutations.DF_female)
cV_plot <- ggplot(all.cv, aes(y = cV, x=type) )+ geom_jitter()+ ggtitle("cv for cell co count, 1000 simulated")+facet_wrap(~sex)
cV_plot

# SC length, bivalent level

don't need to remake permuted DFs, reuse the DFs:  BIG.LIST_w.rank, BIG.DF.LIST_no.rank, BIG.LIST_w.rank_female and BIG.DF.LIST_no.rank_female.

```{r permutations.sc, echo=FALSE, eval=FALSE}

```{r sum.stat.SClength, echo=FALSE}

#Calq SC cV for the SC length FEMALE
SCcv.val.DF_rank.female <- data.frame(  cV = rep(0, length(BIG.LIST_w.rank_female) ) ) #first initialize the DF results will go in outside of loop
for(j in 1:length(BIG.LIST_w.rank_female)){  #inside loop, move thru the LISTs of DFs
  #print(j)
  #fill in the cells of given index
  SCcv.val.DF_rank.female$cV[j] <-cv(  BIG.LIST_w.rank_female[[j]]$SC.length ) #for each
  }

#Calq SC cV for no rank
SCcv.val.DF_no.rank.female <- data.frame(  cV = rep(0, length(BIG.DF.LIST_no.rank_female) ) ) #first initialize the DF results will go in outside of loop
for(i in 1:length(BIG.DF.LIST_no.rank_female)){  #inside loop, move thru the LISTs of DFs
  #print(i)
  #fill in the cells of given index
  SCcv.val.DF_no.rank.female$cV[i] <-cv(  BIG.DF.LIST_no.rank_female[[i]]$SC.length ) #for each 
}

#merge + plots of the cvs
#10 and 10 rows from the permuted
SCcv.val.DF_rank.female$type <- "sim w.rank"
colnames(SCcv.val.DF_rank.female) <- c("cV","type" )

SCcv.val.DF_no.rank.female$type <- "sim no rank"
colnames(SCcv.val.DF_no.rank.female) <- c("cV", "type")

#then add the real values
real.vals.cv.SC_female <- data.frame(female.biv.count_table$cv_SC.length)
real.vals.cv.SC_female$type <- "real"
colnames(real.vals.cv.SC_female) <- c("cV", "type")

#merge and plots
cV.SC_permutations.DF_female <- rbind(SCcv.val.DF_rank.female, SCcv.val.DF_no.rank.female, real.vals.cv.SC_female)

#MALE --BIG.LIST_w.rank, BIG.DF.LIST_no.rank,
#Calq cV for the SC length
SCcv.val.DF_rank.male <- data.frame(  cV = rep(0, length(BIG.LIST_w.rank) ) ) #first initialize the DF results will go in outside of loop
for(j in 1:length(BIG.LIST_w.rank)){  #inside loop, move thru the LISTs of DFs
  #print(j)
  #fill in the cells of given index
  SCcv.val.DF_rank.male$cV[j] <-cv(  BIG.LIST_w.rank[[j]]$SC.length ) #for each
  }

#Calq cV for no rank
SCcv.val.DF_no.rank.male <- data.frame(  cV = rep(0, length(BIG.DF.LIST_no.rank) ) ) #first initialize the DF results will go in outside of loop
for(i in 1:length(BIG.DF.LIST_no.rank)){  #inside loop, move thru the LISTs of DFs
  #print(i)
  #fill in the cells of given index
  SCcv.val.DF_no.rank.male$cV[i] <-cv(  BIG.DF.LIST_no.rank[[i]]$SC.length ) #for each 
}

#merge + plots of the cvs
#10 and 10 rows from the permuted
SCcv.val.DF_rank.male$type <- "sim w.rank"
colnames(SCcv.val.DF_rank.male) <- c("cV","type" )

SCcv.val.DF_no.rank.male$type <- "sim no rank"
colnames(SCcv.val.DF_no.rank.male) <- c("cV", "type")

#then add the real values-- male.biv.count_table
real.vals.cv.SC_male <- data.frame(male.biv.count_table$cv_SC.length)
real.vals.cv.SC_male$type <- "real"
colnames(real.vals.cv.SC_male) <- c("cV", "type")

#merge and plots
cV.SC_permutations.DF_male <- rbind(SCcv.val.DF_rank.male, SCcv.val.DF_no.rank.male, real.vals.cv.SC_male)
cV.SC_permutations.DF_male$sex <- "male"
cV.SC_permutations.DF_female$sex <- "female"  #cV.SC_permutations.DF_female
all_cv.SC <- rbind(cV.SC_permutations.DF_female, cV.SC_permutations.DF_male)

cV.SC_plot <- ggplot(all_cv.SC, aes(y = cV, x=type) )+ geom_jitter()+ ggtitle("cv of within cell SC lengths, 1000 permutations")+facet_wrap(~sex)
```

```{r permuted.v.real, echo=FALSE, eval=FALSE}
for( o in 1:nrow(DF.permutations_CO.count) ) {
  DF.permutations_CO.count$var_CO.count[o] <- var(as.numeric(DF.permutations_CO.count[o,2:20]))
  }

@@

# Junk

```{r junk, eval=FALSE}
DF.permutations <- data.frame( nuc.sim = seq(1:24), rank1 = replicate(24, ""),rank2= replicate(24, ""),
                       rank3= replicate(24, ""),     rank4= replicate(24, ""),
                       rank5= replicate(24, ""),   rank6= replicate(24, ""),
                       rank7= replicate(24, ""), rank8= replicate(24, ""),
                       rank9= replicate(24, ""), rank10= replicate(24, ""),
                       rank11= replicate(24, ""),     rank12= replicate(24, ""),
                       rank13= replicate(24, ""),     rank14= replicate(24, ""),
                       rank15= replicate(24, ""),     rank16= replicate(24, ""),
                       rank17= replicate(24, ""),rank18= replicate(24, ""),rank19= replicate(24, "")
                       )

#permutations -- for SC
